---
title: "Chapter 2 Names and values"
author: "Morgan Grovenburg, Retention Specialist"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include= FALSE}
# Install packages only once
#install.packages("lobstr")

library(lobstr)
```


## 2.1

### Quiz

#### 1. Given the following data frame, how do I create a new column called “3” that contains the sum of `1` and `2`? You may only use `$`, not `[[`. What makes `1`, `2`, and `3` challenging as variable names?

```{r}
df <- data.frame(runif(3), runif(3))
names(df) <- c(1, 2)

df$`3` <- df$`1` + df$`2`
```

#### 2. In the following code, how much memory does `y` occupy?

```{r}
x <- runif(1e6)
y <- list(x, x, x)
```



#### 3. On which line does `a` get copied in the following example?

```{r}
a <- c(1, 5, 3, 2)
b <- a
b[[1]] <- 10
```

### Prerequisites

```{r}
library(lobstr)
```

## 2.2

### 2.2.2 Exercises

#### 1. Explain the relationship between `a`, `b`, `c` and `d` in the following code:

```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10

obj_addr(a)
obj_addr(b)
obj_addr(c)
obj_addr(d)
```

#### 2. The following code accesses the mean function in multiple ways. Do they all point to the same underlying function object? Verify this with `lobstr::obj_addr()`.

```{r}
lobstr::obj_addr(mean)
lobstr::obj_addr(base::mean)
lobstr::obj_addr(get("mean"))
lobstr::obj_addr(evalq(mean))
lobstr::obj_addr(match.fun("mean"))
```



```{r}
x1 <- 1
x2 <- 1
obj_size(x1)
obj_size(x1, x2)

y1 <- "ABC"
y2 <- "ABC"
obj_size(y1)
obj_size(y1, y2)

```

